RationalGRL: A Framework for Argumentation and Goal Modeling

### 2018-08-29 Response to reviewers2.txt

===== ORIGINAL COMMENT #3
I think that the paper should compare the proposed argumentation structure at least with the beliefs in GRL. In general, how does this argumentation approach really differ from one based on beliefs and, in particular, belief revision? Assume that an argument is a belief of some stakeholder revised by another argument, which is a belief of some other stakeholder?

===== ORIGINAL REPLY #3
The connection between argumentation and belief revision is interesting, especially from a theoretical point of view, and in knowledge representation and reasoning this is a popular topic of research (see references 5-7 below). However, since studying relations between argumentation and belief revision does not seem directly related to our current framework and seems more interesting from a formal logical point of view, we have left this out of the discussion in our paper, instead choosing to focus on a comparison with beliefs in GRL.

====== REPLY
In our first revision, we already added a brief comparison between arguments in RationalGRL and beliefs in GRL in the related work section (under "Beliefs in GRL"). We have moved these paragraphs to "Goal Modeling" in section 8.1, and further extended and sharpened our discussion and comparison with GRL beliefs. Our main argument, which is now fully in the article, is that in GRL, beliefs are more of an afterthought: they have no formal semantics and it is not possible to further reason with them (i.e. given indicated conflicts between beliefs compute ways in which beliefs can be revised). Furthermore, we briefly discuss belief revision and the possibilities this may offer for future research. We still believe that discussing the relations between formal argumentation from AI and belief revision postulates from AI is not directly suited for the current (RE) audience. A more detailed comparison between RationalGRL and a framework based on belief revision would require us to develop a new belief revision framework connected to GRL and then model, for example, the case study or an extended example using this new belief revision framework for GRL. This would provide enough material for a new paper.

### 2018-08-29 validation.tex
typo's

In addition, we wanted to know whether the RationalGRL tool was difficult or easy to use. Note that we did not aim to conduct a usability study for the RationalGRL tool. Rather, we were interested to know if the tool was clearly very easy or difficult to use, as this could influence the participants ideas about the RationalGRL framework and language -- a very nice and easy to use tool tends to make people more positive twoards a particular modelling language, whereas irritations about a bad or buggy tool will lead to a more negative disposition. This leads to the following general hypothesis:

@@

For part 2, we provided a small part of a transcript and some context information (see Appendix~\ref{sect:survey}) and asked the participants to model this in the tool and take a screenshot of their final model. The idea is that the participants are ``present'' at a discussion about the early-stage requirements and are asked to model the goal model corresponding to these requirements.

For part 3, we provided the participants with a survey\footnote{https://goo.gl/forms/fDSMUnAV20wy7kbY2} . The survey starts with general questions about the participant (experience etc.). It then asks the following questions about the RationalGRL tool, asking the participants to rate various aspects of the tool on a Likert scale of 1 (very difficult) to 5 (very easy):
\begin{itemize}
\item[Q1] Was it easy or difficult to get started with the RationalGRL tool?
\item[Q2] Was the details pane (containing details of an element, critical questions, etc) easy or difficult to use?
\item[Q3] Was it easy or difficult to understand the way in which the status of arguments and other elements is determined?
\item[Q4] Did you find it easy or difficult to model the example discussion using RationalGRL?
\end{itemize}
We also ask open questions about the strengths and weaknesses of the tool, possible improvements and whether the participant thinks the tool could in the future be used in practice.

>>>>

In addition, we wanted to know whether the RationalGRL tool was difficult or easy to use. Note that we did not aim to conduct a usability study for the RationalGRL tool. Rather, we were interested to know if the tool was clearly very easy or difficult to use, as this could influence the participants ideas about the RationalGRL framework and language -- a very nice and easy to use tool tends to make people more positive towards a particular modelling language, whereas irritations about a bad tool will lead to a more negative disposition. This leads to the following general hypothesis:

@@

For part 2, we provided a small part of a transcript and some context information (see Appendix~\ref{sect:survey}) and asked the participants to model this in the tool and take a screenshot of their final model. The idea is that the participants act as if they are ``present'' at a discussion about the early-stage requirements and are asked to model the goal model corresponding to these requirements.

For part 3, we provided the participants with a survey\footnote{https://goo.gl/forms/fDSMUnAV20wy7kbY2}. The survey starts with general questions about the participant (experience etc.). It then asks the following questions about the RationalGRL tool, asking the participants to rate various aspects of the tool on a Likert scale of 1 (very difficult) to 5 (very easy):
\begin{itemize}
\item[Q1] Was it easy or difficult to get started with the RationalGRL tool?
\item[Q2] Was the details pane (containing details of an element, critical questions, etc) easy or difficult to use?
\item[Q3] Was it easy or difficult to understand the way in which the status of arguments and other elements is determined?
\item[Q4] Did you find it easy or difficult to model the example discussion using RationalGRL?
\end{itemize}
We also ask open questions about the strengths and weaknesses of the tool, possible improvements and whether the participant thinks the tool could in the future be used in practice.
